\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-18 paper/paper.tex
Added moooore to related work.

\ednote{DENIS DOES THIS.}

@@

\section{Limitations and Possible Extensions}
\label{sec:limitations}
Due to time constraints, this paper is not extensive enough to cover all optimization possibilities. This section will therefore point out limitations of our algorithm and ideas on how to overcome them.

>>>>

The mapping of underwater structures is a prominent task in underwater robotics. But only a few papers deal with the actual algorithm which is used to guide the robot during its exploration and mapping. Moreover we could not find any previous work that deals with guidance algorithm for the mapping of a horizontal structure via an autonomous underwater robot.\\

One paper that deals with the actual guiding algorithm is \textit{A behavior-based architecture for autonomous underwater exploration} \cite{rosenblatt2002behavior}. There the authors are using a behavior-based control architecture to safely guide a robot through a reef. Their robot follows a rope on the sea floor by utilizing a camera to get optical input. The rope acts in their case as a tool for collision avoidance and path planning as it can be safely laid out by humans beforehand.\\

Another paper which deals with the actual guiding of the robot is \textit{3-D terrain covering and map building algorithm for an AUV} \cite{lee20093}. In this paper the authors deal with the guidance and mapping of the ocean floor where we have multiple island or underwater mountains around. There the approach is in essence to explore the whole search space by exploring iteratively a plane for each depth level.\\

Moreover many papers deal with cooperative exploration with multiple robots and the path planning for those robots. This does not apply well to our problem though, as we are only dealing with one robot and do not have to account for problems and challenges like the optimal division of work.~\cite{wu2012robust}

Most other papers which deal with the actual guidance do so in combination with related mapping techniques like SLAM one example here is \cite{makarenko2002experiment}.

@@

\section{Limitations and Possible Extensions}
\label{sec:limitations}
Due to time constraints, this paper is not extensive enough to cover all optimization possibilities. This section will therefore point out limitations of our algorithm and ideas on how to implement these.
